#### Loading the data

```{r setup-2-3-1}
# Load the tidyverse 
library(tidyverse)

# Data path, works alone or from the main document
data_dir <- if (dir.exists("data")) "data" else "../../data"
```

```{r look-snore-raw}
# Look at the raw file to identify the separator and the header
readLines(file.path(data_dir, "snore.txt"), n = 5)
```

```{r load-snore}
# Read the tab-separated file
snore <- read.delim(file.path(data_dir, "snore.txt"))

# Type of each variable and summary statistics
str(snore)
summary(snore)

# Number of people in each category
table(snore$sex)
table(snore$snore)
table(snore$tabac)
```

#### Description of the data

The file contains 100 people and 7 variables, with no missing values: age (years), weight (kg), height (cm), alcool (unit not specified), sex (H = man, F = woman), snore (O = yes, N = no) and tabac (O = smoker, N = non-smoker). Units of weight and height are not given but were deduced from the range of values. The sample includes 75 men and 25 women, 35 snorers and 64 smokers.
**Reference:** data provided by the course instructor (see Data sources).
#### Measure of corpulence

Since weight depends on height, corpulence was assessed with the body mass index (BMI = weight / height²).
**Reference:** World Health Organization (2000).

```{r compute-bmi}
# BMI in kg/m², with height converted from cm to m
snore$bmi <- snore$weight / (snore$height / 100)^2
summary(snore$bmi)
```