#### Are snorers fatter?

```{r normality-bmi-snore}
shapiro.test(snore$bmi[snore$snore == "O"])
shapiro.test(snore$bmi[snore$snore == "N"])
```

Normality of BMI was rejected in both groups (p < 0.05), so snorers and non-snorers were compared with the Mann-Whitney test.

```{r test-bmi-snore}
tapply(snore$bmi, snore$snore, median)
wilcox.test(bmi ~ snore, data = snore)
```

```{r plot-bmi-snore}
ggplot(snore, aes(x = snore, y = bmi)) +
  geom_boxplot(outlier.shape = NA) +
  geom_jitter(width = 0.1, height = 0, alpha = 0.5) +
  scale_x_discrete(labels = c("N" = "Non-snorers", "O" = "Snorers")) +
  labs(title = "BMI of snorers and non-snorers", x = "", y = "BMI (kg/m²)") +
  theme_bw()
```

Snorers did not have a higher BMI than non-snorers (median 28.1 kg/m² in both groups, Mann-Whitney test, p > 0.05). The data do not confirm the stereotype that snorers are fatter.


#### Do snorers drink or smoke more?

```{r normality-alcool-snore}
shapiro.test(snore$alcool[snore$snore == "O"])
shapiro.test(snore$alcool[snore$snore == "N"])
```

Normality of alcohol consumption was rejected in both groups (p < 0.05), so snorers and non-snorers were compared with the Mann-Whitney test.

```{r test-alcool-snore}
tapply(snore$alcool, snore$snore, median)
wilcox.test(alcool ~ snore, data = snore)
```

```{r plot-alcool-snore}
ggplot(snore, aes(x = snore, y = alcool)) +
  geom_boxplot(outlier.shape = NA) +
  geom_jitter(width = 0.1, height = 0, alpha = 0.5) +
  scale_x_discrete(labels = c("N" = "Non-snorers", "O" = "Snorers")) +
  labs(title = "Alcohol consumption of snorers and non-snorers", x = "", y = "Alcohol (unit not specified)") +
  theme_bw()
```

Snorers drank significantly more alcohol than non-snorers (median 4 vs 0, Mann-Whitney test, p < 0.05). The data confirm the stereotype that snorers drink more.

Since both variables are categorical, smoking was compared between snorers and non-snorers with a chi-squared test, after checking that all expected counts were at least 5.

```{r test-tabac-snore}
tab_snore <- table(snore$snore, snore$tabac, dnn = c("snore", "tabac"))
tab_snore
round(prop.table(tab_snore, margin = 1) * 100, 1)
test_snore <- chisq.test(tab_snore)
test_snore$expected
test_snore
```

```{r plot-tabac-snore}
ggplot(snore, aes(x = snore, fill = tabac)) +
  geom_bar(position = "fill", color = "black") +
  scale_x_discrete(labels = c("N" = "Non-snorers", "O" = "Snorers")) +
  scale_fill_grey(start = 0.9, end = 0.4, labels = c("N" = "Non-smoker", "O" = "Smoker")) +
  scale_y_continuous(labels = scales::percent) +
  labs(title = "Proportion of smokers among snorers and non-snorers", x = "", y = "Proportion", fill = "") +
  theme_bw()
```

Snorers did not smoke more than non-snorers (57.1% vs 67.7% of smokers, chi-squared test, p > 0.05). The data do not confirm the stereotype that snorers smoke more


#### Are men fatter?

```{r normality-bmi-sex}
shapiro.test(snore$bmi[snore$sex == "H"])
shapiro.test(snore$bmi[snore$sex == "F"])
```

Normality of BMI was rejected in both groups (p < 0.05), so men and women were compared with the Mann-Whitney test.

```{r test-bmi-sex}
tapply(snore$bmi, snore$sex, median)
wilcox.test(bmi ~ sex, data = snore)
```

```{r plot-bmi-sex}
ggplot(snore, aes(x = sex, y = bmi)) +
  geom_boxplot(outlier.shape = NA) +
  geom_jitter(width = 0.1, height = 0, alpha = 0.5) +
  scale_x_discrete(labels = c("F" = "Women", "H" = "Men")) +
  labs(title = "BMI of men and women", x = "", y = "BMI (kg/m²)") +
  theme_bw()
```

Men did not have a higher BMI than women (median 28.1 vs 27.7 kg/m², Mann-Whitney test, p > 0.05). The data do not confirm the stereotype that men are fatter


#### Do women smoke less?

Since both variables are categorical, smoking was compared between men and women with a chi-squared test, after checking that all expected counts were at least 5

```{r test-tabac-sex}
tab_sex <- table(snore$sex, snore$tabac, dnn = c("sex", "tabac"))
tab_sex
round(prop.table(tab_sex, margin = 1) * 100, 1)
test_sex <- chisq.test(tab_sex)
test_sex$expected
test_sex
```

```{r plot-tabac-sex}
ggplot(snore, aes(x = sex, fill = tabac)) +
  geom_bar(position = "fill", color = "black") +
  scale_x_discrete(labels = c("F" = "Women", "H" = "Men")) +
  scale_fill_grey(start = 0.9, end = 0.4, labels = c("N" = "Non-smoker", "O" = "Smoker")) +
  scale_y_continuous(labels = scales::percent) +
  labs(title = "Proportion of smokers among men and women", x = "", y = "Proportion", fill = "") +
  theme_bw()
```

Women smoked significantly less than men (40% vs 72% of smokers, chi-squared test, p < 0.05). The data confirm the stereotype that women smoke less.