#### Does the treatment have an effect?

Yes, Perf increased significantly after rehabilitation (Wilcoxon signed-rank test, p < 0.05), assuming that the rows are ordered by patient. The comparison, the test and the graph supporting this answer are detailed below.


#### What comparison are you going to make?

The Before and After values were measured on the same 8 patients, so we compared perf Before and After rehabilitation with a paired comparison. The data file contains no patient identifier, so we assumed that the rows are in the same patient order in both groups.

#### Which test will you use? Parametric or non-parametric?

For a paired comparison, normality is checked on the differences between the two measures of each patient.

```{r normality-prepost}
# Separate the Before and After values
before <- prepost$perf[prepost$time == "Before"]
after  <- prepost$perf[prepost$time == "After"]

# Shapiro-Wilk test on the differences (After minus Before)
shapiro.test(after - before)
```

Normality of the differences was not rejected (p > 0.05), but with only 8 patients the Shapiro-Wilk test has very low power, so we used the non-parametric Wilcoxon signed-rank test.

```{r compare-prepost}
# Wilcoxon signed-rank test (paired, non-parametric)
wilcox.test(after, before, paired = TRUE)
```


#### Which graph illustrates the effect of the treatment?

A line plot connecting the two measures of each patient shows the individual change, which suits a paired design.

```{r plot-prepost}
# Patient identifier, assuming the same patient order in both groups
prepost$patient <- rep(1:8, times = 2)

# Order the time axis: Before then After
prepost$time <- factor(prepost$time, levels = c("Before", "After"))

# One line per patient, from Before to After
ggplot(prepost, aes(x = time, y = perf, group = patient)) +
  geom_line() +
  geom_point() +
  labs(title = "Perf before and after rehabilitation",
       x = "Time",
       y = "Perf (unit not specified)") +
  theme_bw()
```

Figure: Perf of each patient before and after rehabilitation. Each line connects the two measures of the same patient, assuming that the rows are ordered by patient. All 8 patients show an increase, ranging from 1 to 5 units.

#### What sentence will you write in your thesis to explain your result?

After the rehabilitation program, perf increased significantly in the 8 patients, with a median increase of 2.5 units (Wilcoxon signed-rank test, p < 0.05), assuming that the rows of the data file are ordered by patient.

This conclusion relies on the assumption that the rows are in the same patient order in both groups. Since the values of each group are sorted in increasing order, this pairing could not be verified, and sorting alone would produce positive differences. The original data with a patient identifier would be needed to confirm this result. Moreover, since the data only include measures before and after the program, we cannot assess whether the effect is lasting.